
The Electoral Democracy Index (v2x_polyarchy) is formed by taking the average of, on the one hand, the weighted average of the indices measuring freedom of association (thick) (v2x_frassoc_thick), clean elections (v2xel_frefair), freedom of expression and alternative sources of information (v2x_free_altinf), elected officials (v2x_elecoff), and suffrage (v2x_suffr) and, on the other, the five-way multiplicative interaction between those indices.
```{r}
library(ggplot2)
library(dplyr)
library(ggthemes)
library(extrafont)
```

```{r}
peru = vdem[vdem$country_name == "Peru",]
subset_peru = peru[,c("year","v2x_polyarchy")]
```

```{r}
subset_peru %>% 
  ggplot(aes(x = year, y = v2x_polyarchy)) + 
  geom_line(size = 1, color = "red") + 
  labs(title = "Electoral Democracy Index - Peru",
       subtitle = "Evolution over time",
       x = "Year",
       y = "Index") +
  
  theme_fivethirtyeight()+
  theme(axis.title = element_text(), text = element_text(family = "Arial Narrow"))

```

```{r}
subset_peru = subset_peru[subset_peru$year > 1980,]
```

```{r}
subset_peru %>% 
  ggplot(aes(x = year, y = v2x_polyarchy)) + 
  geom_line(size = 1, color = "red") + 
  labs(title = "Electoral Democracy Index - Peru",
       subtitle = "Evolution over time (1980 - 2020)",
       x = "Year",
       y = "Index") +
  
  theme_fivethirtyeight()+
  theme(axis.title = element_text(), text = element_text(family = "Arial Narrow"))

```

